Calculating Entropies With Nested Sampling

### 2017-01-15 paper/ms.tex
Some sections, to remind myself of what to discuss

\DeclareUnicodeCharacter{00A0}{ }
\newcommand{\x}{\boldsymbol{x}}
\renewcommand{\d}{\boldsymbol{d}}

@@

@@

\acknowledgments{Acknowledgements}

>>>>

\DeclareUnicodeCharacter{00A0}{ }

\definecolor{orange}{rgb}{1, 0.5, 0}

\renewcommand{\d}{\boldsymbol{d}}
\newcommand{\todo}{\color{orange} \bf}
\newcommand{\x}{\boldsymbol{x}}

@@

The

\subsection{Mutual information}

@@

\subsection{The sequence of $X$ values}
When $N=1$, the sequence of $X$ values is a Poisson process.

\citet{Walter2015} showed how this view of the NS sequence of points
can be used to construct a
version of NS that produces unbiased estimates of the marginal likelihood.
However, it can also be used to construct an unbiased estimator of
a log-probability, which is more relevant to information theoretic
quantities.

\section{The algorithm}

\section{Example 1: A trivial bivariate gaussian}

\section{Example 2: Measuring the period of an oscillating signal}

The multimodality of the posterior here raises an interesting issue. Is
the question we really want answered ``what is the value of $T$
{\bf precisely}?'', to which the mutual information relates?
Most practicing scientists would not feel particularly informed to learn
that the vast majority of possibilities had been ruled out, if the
posterior still consisted of several widely separated modes!

Perhaps, in some applications, a more appropriate question is
``what is the value of $T$ to within $\pm$ 10\%''
{\todo or something like that.}

\section{Example 3: TBD}

\acknowledgments{Acknowledgements}
It is a pleasure to thank the following people for interesting and helpful
conversations about this topic: Ruth Angus (Flatiron Institute),
Ewan Cameron (Oxford), David Hogg (NYU), Kevin Knuth (SUNY Albany),
Iain Murray (Edinburgh).
